Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-02-04 paper/main.tex
paper s5

In Section~\ref{sec:permutations}, we highlighted the important difference between rankings and orderings, usually neglected in the optimization literature. Statistical models (Borda or the \ken distance) are usually defined for rankings while the optimization literature usually considers orderings. An example of such confusion is the claim that Swap distance is the same metric as  the \ken distance, which is false except for particular permutations. In reality, the \emph{swap} distance is the \ken distance of the inverted permutations.

@@

The red

>>>>

In Section~\ref{sec:permutations}, we highlighted the important difference between rankings and orderings, usually neglected in the optimization literature. Statistical models (Borda or the \ken distance) are usually defined for rankings while the optimization literature usually considers orderings. For example, the Swap distance $d_s(\sigma,\pi)$ is the \ken distance counterpart in optimization, $d_s(\sigma,\pi) = d(\sigma^{-1}, \pi^{-1})$. The concepts of rankings and orderings are usually confused of ignored. An example of such confusion is the claim that Swap distance is the same metric as  the \ken distance, which is false except for particular permutations. In reality, the \emph{swap} distance is the \ken distance of the inverted permutations.

@@

The red and the gold lines correspond to CEGO, the original and our modified versions
